### 2017-10-23 paper/sections/1_introduction.tex
paper: jeff comments/citations and fix figures
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What did we do
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a potential
setup in our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art
architectures.  The HDFS\footnote{HDFS itself is not directly evaluated in this
paper, although the HDFS semantics and their performance is explored
in~\S\ref{sec:use-case-1}} subtree has weaker consistency than strong
consistency because it does not guarantee that all updates are immediately seen
by all servers; the BatchFS and RAMDisk subtrees are decoupled from the global
namespace and have similar consistency/durability behavior to those systems;
and the POSIX IO subtree retains the rigidity of POSIX IO's strong consistency.
Subtrees without policies inherit the consistency/durability semantics of the
parent and future work will examine embeddable or inheritable policies.

@@

  \item A framework and API for assigning consistency/durability policies 
  to subtrees in the file system namespace; this lets users navigate
  the trade-offs of different metadata protocols.

  \item This framework lets subtrees with different semantics co-exist in a
  global namespace. We show how this scales further and performs better than
  systems that use one strategy for the entire namespace

@@

The last contribution lays the groundwork for future work on our prototype. It
improves the current practice of mounting different storage systems in a global
namespace because there is no need to provision dedicated storage clusters to
applications or move data between these systems.  For example, the results of a
Hadoop job do not need to be migrated into CephFS for other processing; instead
the user can change the semantics of the HDFS subtree into a CephFS subtree.
This may cause metadata/data movement to make things strongly consistent again
but this is superior to moving all data across file system boundaries. We
enable studies that adjust these semantics over {\it time and space}, where
subtrees can change their semantics and migrate around the cluster without ever
moving the data they reference.

% Results
The results in this paper lay the groundwork for such a system and confirm the
assertions of ``clean-state" research that decouple namespaces; specifically
that the technique drastically improves performance (104\(\times\) speed up).
We go a step further by quantifying the costs of merging updates (7\(\times\)
slow down) and maintaining durability (\(10\times\) slow down). In our
prototype, we get an 8\(\times\) speedup and can scale to twice as many servers
when we assign a more relaxed form of consistency and durability to a subtree
with a create-heavy workload.  We build on Ceph because it is used in
cloud-based and data center systems and has a presence in HPC~\cite{}.  More
importantly,  we use Ceph as a platform for exploring related work over the
same storage system, which facilitates an apples-to-apples comparison of the
strategies themselves.

>>>>

% What did we do
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a potential
setup in our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art
architectures.  The HDFS\footnote{HDFS itself is not directly evaluated in this
paper, although the semantics and their performance is explored
in~\S\ref{sec:use-case-1}.} subtree has weaker than strong consistency because
for performance it lets clients read files opened for
writing~\cite{hakimzadeh:dais14-hdfs-consistency}, which means that not all
updates are immediately seen by all servers; the BatchFS and RAMDisk subtrees
are decoupled from the global namespace and have similar consistency/durability
behavior to those systems; and the POSIX IO subtree retains the rigidity of
POSIX IO's strong consistency.  Subtrees without policies inherit the
consistency/durability semantics of the parent and future work will examine
embeddable or inheritable policies.

@@

  \item A framework and API for assigning consistency/durability policies 
  to subtrees in the file system namespace; this lets users navigate
  the trade-offs of different metadata protocols on the same storage system.

  \item This framework lets subtrees with different semantics co-exist in a
  global namespace. We show how this scales further and performs better than
  systems that use one strategy for the entire namespace .

@@

The last contribution lays the groundwork for future work on our prototype. It
is better than the current practice of mounting different storage systems in a global
namespace because there is no need to provision dedicated storage clusters to
applications or move data between these systems.  For example, the results of a
Hadoop job do not need to be migrated into CephFS for other processing; instead
the user can change the semantics of the HDFS subtree into a CephFS subtree.
This may cause metadata/data movement to make things strongly consistent again
but this is superior to moving all data across file system boundaries. We
enable studies that adjust these semantics over {\it time and space}, where
subtrees can change their semantics and migrate around the cluster without ever
moving the data they reference.

% Results
The results in this paper lay the groundwork for such a system and confirm the
assertions of ``clean-state" research that decouple namespaces; specifically
that the technique drastically improves performance (104\(\times\) speed up).
We go a step further by quantifying the costs of merging updates (7\(\times\)
slow down) and maintaining durability (\(10\times\) slow down). In our
prototype, we get an 8\(\times\) speedup and can scale to twice as many clients
when we assign a more relaxed form of consistency and durability to a subtree
with a create-heavy workload.  We use Ceph as a prototyping platform because it
is used in cloud-based and data center systems and has a presence in
HPC~\cite{wang:pdsw13-ceph-hpc}.

### 2017-10-23 paper/sections/2_related_work.tex
paper: jeff comments/citations and fix figures
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

The bottlenecks associated with accessing POSIX IO file system metadata are not limited
to HPC workloads and the same challenges that plagued these systems for years are
finding their way into the cloud. Workloads that deal with many small files
({\it e.g.}, log processing and database

@@

the metadata service. The biggest challenge is that whenever a file
is touched the client must access the file's metadata and maintaining a file
system namespace imposes small, frequent accesses on the underlying storage

@@

abad:techreport2012-fstrace, abad:ucc2012-mimesis,
alam:pdsw2011-metadata-scaling, weil:osdi2006-ceph}. 
%There are two approaches
%for improving the performance of metadata access.

@@

%% fixed resource per work unit)
%% CITEME
%One approach for improving metadata performance and scalability is to alleviate
%overloaded servers by load balancing metadata IO across a cluster. Common
%techniques include partitioning metadata when there are many writes and
%replicating metadata when there are many reads. For example, IndexFS~\cite{ren:sc2014-indexfs} partitions

@@

%Despite the performance benefits these techniques add complexity and jeopardize
%the robustness and performance characteristics of the metadata service because
%the systems now need (1) policies to guide the migration decisions and (2)
%mechanisms to address inconsistent states across servers.

@@

%% policies
%Setting policies for migrations is arguably more difficult than adding the
%migration mechanisms themselves.  For example, IndexFS and CephFS use the
%GIGA+~\cite{patil:fast2011-giga} technique for partitioning directories at a predefined
%threshold and using lazy synchronization to redirect queries to the server that
%``owns" the targeted metadata.  Determining when to partition directories and
%when to migrate the directory fragments are policies that vary between systems:
%GIGA+ partitions directories when the size reaches a certain number of files
%and migrates directory fragments immediately; CephFS partitions directories
%when they reach a threshold size or when the write temperature reaches a
%certain value and migrates directory fragments when the hosting server has more
%load than the other servers in the metadata cluster. Another policy is when and
%how to replicate directory state; ShardFS replicates immediately and
%pessimistically while CephFS replicates only when the read temperature reaches
%a threshold.  There is a wide range of policies and it is difficult to maneuver
%tunables and hard-coded design decisions.

@@

%% addressing inconsistency
%In addition to the policies, distributing metadata across a cluster requires
%distributed transactions and cache coherence protocols to ensure strong
%consistency ({e.g.}, POSIX IO).  For example, ShardFS pessimistically replicates
%directory state and uses optimistic concurrency control for conflicts; namely
%it does the operation and if there is a conflict at verification time it falls
%back to two-phase locking.  Another example is IndexFS's inode cache which
%reduces RPCs by caching ancestor paths -- the locality of this cache can be
%thrashed by random reads but performs well for metadata writes. For
%consistency, writes to directories in IndexFS block until the lease expires
%while writes to directories in ShardFS are slow for everyone as it either
%requires serialization or locking with many servers; reads in IndexFS are
%subject to cache locality while reads in ShardFS always resolve to 1 RPC.
%Another example of the overheads of addressing inconsistency is how CephFS
%maintains client sessions and inode caches for capabilities (which in turn make
%metadata access faster). When metadata is exchanged between metadata servers
%these sessions/caches must be flushed and new statistics exchanged with a
%scatter-gather process; this halts updates on the directories and blocks until
%the authoritative metadata server responds.  These protocols are discussed in
%more detail in the next section but their inclusion here is a testament to the
%complexity of migrating metadata.

@@

%%server. Zooming in on monotonic writes: if permissions increase it executes on
%%a primary then non-primary, if permissions decrease it executes on all

@@

For (1), state-of-the-art systems manage consistency in non-traditional ways:
IndexFS maintains the global namespace but blocks operations from other clients
until the first client drops the lease, BatchFS does operations on a snapshot
of the namespace and merges batches of operations into the global namespace,
and DeltaFS never merges back into the global namespace. The merging for
BatchFS is done by an auxiliary metadata server running on the client and
conflicts are resolved by the application. Although DeltaFS never explicitly
merges, applications needing some degree of ground truth can either manage
consistency themselves on a read or add a bolt-on service to manage the
consistency.

For (2), if the client fails and stays down, all metadata operations on the
decoupled namespace are lost. If the client recovers, the on-disk structures
(for BatchFS and DeltaFS this is the SSTables used in TableFS) can be
recovered. In other words, the clients have state that cannot be recovered if
the node stays failed and any progress will be lost. This scenario is a
disaster for checkpoint-restart where missed cycles may cause the checkpoint to
bleed over into computation time.

For (3), decoupled namespace approaches sacrifice POSIX IO going as far as
requiring the application to link against the systems they want to talk to. In
today's world of software defined caching, this can be a problem for large data
centers with many types and tiers of storage. Despite well-known performance
problems POSIX IO and REST are the dominant APIs for data transfer.

>>>>

The bottlenecks associated with accessing POSIX IO file system metadata are not
limited to HPC workloads and the same challenges that plagued these systems for
years are finding their way into the cloud. Workloads that deal with many small
files ({\it e.g.}, log processing and database

@@

the metadata service. The biggest challenge is that whenever a file is touched
the client must access the file's metadata and maintaining a file system
namespace imposes small, frequent accesses on the underlying storage

@@

abad:ucc2012-mimesis, alam:pdsw2011-metadata-scaling, weil:osdi2006-ceph}. 
%There are two approaches for improving the performance of metadata access.

@@

%% fixed resource per work unit) % CITEME One approach for improving metadata
%performance and scalability is to alleviate overloaded servers by load
%balancing metadata IO across a cluster. Common techniques include partitioning
%metadata when there are many writes and replicating metadata when there are
%many reads. For example, IndexFS~\cite{ren:sc2014-indexfs} partitions

@@

%Despite the performance benefits these techniques add complexity and
%jeopardize the robustness and performance characteristics of the metadata
%service because the systems now need (1) policies to guide the migration
%decisions and (2) mechanisms to address inconsistent states across servers.

@@

%% policies Setting policies for migrations is arguably more difficult than
%adding the migration mechanisms themselves.  For example, IndexFS and CephFS
%use the GIGA+~\cite{patil:fast2011-giga} technique for partitioning
%directories at a predefined threshold and using lazy synchronization to
%redirect queries to the server that ``owns" the targeted metadata.
%Determining when to partition directories and when to migrate the directory
%fragments are policies that vary between systems: GIGA+ partitions directories
%when the size reaches a certain number of files and migrates directory
%fragments immediately; CephFS partitions directories when they reach a
%threshold size or when the write temperature reaches a certain value and
%migrates directory fragments when the hosting server has more load than the
%other servers in the metadata cluster. Another policy is when and how to
%replicate directory state; ShardFS replicates immediately and pessimistically
%while CephFS replicates only when the read temperature reaches a threshold.
%There is a wide range of policies and it is difficult to maneuver tunables and
%hard-coded design decisions.

@@

%% addressing inconsistency In addition to the policies, distributing metadata
%across a cluster requires distributed transactions and cache coherence
%protocols to ensure strong consistency ({e.g.}, POSIX IO).  For example,
%ShardFS pessimistically replicates directory state and uses optimistic
%concurrency control for conflicts; namely it does the operation and if there
%is a conflict at verification time it falls back to two-phase locking.
%Another example is IndexFS's inode cache which reduces RPCs by caching
%ancestor paths -- the locality of this cache can be thrashed by random reads
%but performs well for metadata writes. For consistency, writes to directories
%in IndexFS block until the lease expires while writes to directories in
%ShardFS are slow for everyone as it either requires serialization or locking
%with many servers; reads in IndexFS are subject to cache locality while reads
%in ShardFS always resolve to 1 RPC.  Another example of the overheads of
%addressing inconsistency is how CephFS maintains client sessions and inode
%caches for capabilities (which in turn make metadata access faster). When
%metadata is exchanged between metadata servers these sessions/caches must be
%flushed and new statistics exchanged with a scatter-gather process; this halts
%updates on the directories and blocks until the authoritative metadata server
%responds.  These protocols are discussed in more detail in the next section
%but their inclusion here is a testament to the complexity of migrating
%metadata.

@@

%%server. Zooming in on monotonic writes: if permissions increase it executes
%on %a primary then non-primary, if permissions decrease it executes on all

@@

For (1), state-of-the-art systems manage consistency in non-traditional ways:
IndexFS maintains the global namespace but blocks operations from other clients
until the first client drops the lease, BatchFS does operations on a snapshot
of the namespace and merges batches of operations into the global namespace,
and DeltaFS never merges back into the global namespace. The merging for
BatchFS is done by an auxiliary metadata server running on the client and
conflicts are resolved by the application. Although DeltaFS never explicitly
merges, applications needing some degree of ground truth can either manage
consistency themselves on a read or add a bolt-on service to manage the
consistency. For (2), if the client fails and stays down, all metadata
operations on the decoupled namespace are lost. If the client recovers, the
on-disk structures (for BatchFS and DeltaFS this is the SSTables used in
TableFS) can be recovered. In other words, the clients have state that cannot
be recovered if the node stays failed and any progress will be lost. This
scenario is a disaster for checkpoint-restart where missed cycles may cause the
checkpoint to bleed over into computation time. For (3), decoupled namespace
approaches sacrifice POSIX IO going as far as requiring the application to link
against the systems they want to talk to. In today's world of software defined
caching, this can be a problem for large data centers with many types and tiers
of storage. Despite well-known performance problems POSIX IO and REST are the
dominant APIs for data transfer.

### 2017-10-23 paper/sections/7_conclusion.tex
paper: jeff comments/citations and fix figures
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Relaxing consistency and durability semantics in the file system is a
double-edged sword. While it achieves better performance and scalability, it
alienates applications that rely on strong consistency and durability. Mounting
other systems to the global namespace is convenient but wastes resources and
incurs data movement.  Cudele lets users assign consistency and durability
guarantees to subtrees in the global namespace, which can be custom fit to the
application. Using Cudele, we show how applications can co-exist and perform
well in a global namespace and lay the groundwork for new systems that
dynamically change consistency/durability guarantees to avoid provisioning
dedicated storage clusters and moving large amounts of data.

>>>>

Relaxing consistency/durability semantics in the file system is a double-edged
sword. While it performs and scales better, it alienates applications that rely
on strong consistency and durability. Mounting other systems to the global
namespace is convenient but wastes resources and incurs data movement.  Cudele
lets users assign consistency/durability guarantees to subtrees in the global
namespace, which can be custom fit to the application. Using Cudele, we show
how applications can co-exist and perform well in a global namespace and lay
the groundwork for new systems that dynamically change consistency/durability
guarantees to avoid provisioning dedicated storage clusters and moving large
amounts of data.
